Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-09-10 analysis/presentation/sim_survey_presentation.Rmd
Tweak interpretations in presentation and clean-up test_survey documentation

<br>

In this scenario,

- Bias is negligible
- Increasing sub-sampling is always benifical
- Sampling fewer fish at more locations appears better than many fish at fewer locations

## Interpretation

Why is there bias? Why is extra sub-sampling sometimes useful and sometimes detrimental?

>>>>

- In this scenario, 
    - Bias is negligible
    - Increasing sub-sampling is always beneficial
        - No age-specific clustering means that one fish is as "effective" as the next
    - Sub-sampling fewer fish at more locations appears better than many fish at fewer locations
        - Though more sub-samples improve perception of the age-distribution, it does little to inform magnitude

Why is there bias in the main scenario? Why is extra sub-sampling sometimes useful / sometimes detrimental?
